Predictive modeling with cross validation

### 2017-08-15 model fitting/cross_validation.Rmd
created new markdown for univariate analysis, stratified model on new_category

```{r, echo = FALSE}
splitPlan <- vtreat::kWayCrossValidation(nrow(x), 5, NULL, NULL)
str(splitPlan)
```

@@

##### Univariate analyses

```{r, include = FALSE}
train1 <- x[splitPlan[[1]]$train, ]

#===================================================================
# Univariate analyses (select variables with p-value < 0.01)
# category 
train1$category <- as.character(train1$category)
train1$category[is.na(train1$category)] <- "Other"
train1$category <- as.factor(train1$category)
cr_cat <- coxph(Surv(time_until_answer, answered) ~ category, data = train1)
summary(cr_cat) # p=0

#===================================================================
# n_images
cr_image <- coxph(Surv(time_until_answer, answered) ~ n_images, data = train1)
summary(cr_image) # p=2.23e-06
train1$new_n_images <- as.character(train1$n_images) # recoding to group questions with >= 6 images 
train1$new_n_images[train1$n_images >= 6] <- ">= 6"
cr_image1 <- coxph(Surv(time_until_answer, answered) ~ new_n_images, data = train1)
summary(cr_image1) # p=6.461e-06

#===================================================================
# n_tags
cr_ntags <- coxph(Surv(time_until_answer, answered) ~ as.factor(n_tags), data = train1)
summary(cr_ntags) # p=2.039e-09
train1$n_tags <- as.factor(train1$n_tags)

#===================================================================
# new_user
cr_user <- coxph(Surv(time_until_answer, answered) ~ as.factor(new_user), data = train1)
summary(cr_user) # p=0
train1$new_user <- as.factor(train1$new_user)

#===================================================================
# weekday
train1$datetime <- as.POSIXct(train1$post_date,origin="1970-01-01")
train1$weekday <- factor(weekdays(train1$datetime), levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))
cr_weekday <- coxph(Surv(time_until_answer, answered) ~ weekday, data = train1)
summary(cr_weekday) # p=0.0006061

#===================================================================
# is_weekend
train1$is_weekend <- FALSE
train1$is_weekend[train1$weekday == "Saturday" | train1$weekday == "Sunday"] <- TRUE
cr_weekend <- coxph(Surv(time_until_answer, answered) ~ is_weekend, data = train1)
summary(cr_weekend) # p=0.001602

#===================================================================
# hour of the day
train1$hour <- as.numeric(format(train1$datetime,"%H"))
cr_hour <- coxph(Surv(time_until_answer, answered) ~ hour, data = train1)
summary(cr_hour) # p=0.3994

#===================================================================
# morning/noon/evening/night?
train1$ampm <- "Night"
train1$ampm[train1$hour >= 5 & train1$hour < 12] <- "Morning"
train1$ampm[train1$hour >= 12 & train1$hour < 17] <- "Afternoon" #noon - 5pm
train1$ampm[train1$hour >= 17 & train1$hour < 20] <- "Evening" #5pm - 8pm
cr_ampm <- coxph(Surv(time_until_answer, answered) ~ ampm, data = train1)
summary(cr_ampm) # p=0.0001333

#===================================================================
# title length
train1$title_length <- str_length(train1$title)
cr_title_len <- coxph(Surv(time_until_answer, answered) ~ title_length, data = train1)
summary(cr_title_len) # p=0.4386

#===================================================================
# text length
train1$text_length <- str_length(train1$text)
cr_text_len <- coxph(Surv(time_until_answer, answered) ~ text_length, data = train1)
summary(cr_text_len) # p=1.477e-14

#===================================================================
# device name length
train1$device_length <- str_length(train1$device)
cr_device_len <- coxph(Surv(time_until_answer, answered) ~ device_length, data = train1)
summary(cr_device_len) # p=0.0113

#===================================================================
# length of sentence until first punctuation mark
train1$length <- str_locate(train1$text, pattern = "[.|?|!]")[,1]
q <- quantile(train1$length, probs = seq(0, 1, by = 0.25), na.rm = TRUE)
train1$text_till_punct <- "none"
train1$text_till_punct[train1$length <= q[3]] <- "short"
train1$text_till_punct[train1$length >= q[3] & train1$length <= q[4]] <- "medium"
train1$text_till_punct[train1$length >= q[4]] <- "long"

cr_tillpunct <- coxph(Surv(time_until_answer, answered) ~ text_till_punct, data = train1)
summary(cr_tillpunct) # p=2.769e-07

#===================================================================
# if text contains any end punctuation
train1$text_contain_punct <- str_detect(train1$text, pattern = "[.|?|!]")
cr_containpun <- coxph(Surv(time_until_answer, answered) ~ text_contain_punct, data = train1)
summary(cr_containpun) # p=8.269e-09
identical(train1$text_contain_punct, train1$contain_punct)

#===================================================================
# if the text ends in a punctuation
train1$text_end_punct <- str_detect(train1$text, pattern = "[.|?|!]$")
cr_endpunct <- coxph(Surv(time_until_answer, answered) ~ text_end_punct, data = train1)
summary(cr_endpunct) # p=0.185

#===================================================================
# if the title ends with a question mark
library(rebus)
train1$title_questionmark <- str_detect(train1$title, pattern = QUESTION %R% END)
cr_title_q <- coxph(Surv(time_until_answer, answered) ~ title_questionmark, data = train1)
summary(cr_title_q) # p=6.55e-15

#===================================================================
# if title begins with "wh"
train1$title_beginwh <- str_detect(str_to_lower(train1$title), pattern = "^wh")
cr_begin <- coxph(Surv(time_until_answer, answered) ~ title_beginwh, data = train1)
summary(cr_begin) # p=0.2241

#===================================================================
# if first letter of title is capitalized
train1$capital_title <- str_detect(as.character(train1$title), pattern = "^[[:upper:]]")
cr_title <- coxph(Surv(time_until_answer, answered) ~ capital_title, data = train1)
summary(cr_title) # p=0.6906

#===================================================================
# if first letter of text is capitalized
train1$capital_text <- str_detect(as.character(train1$text), pattern = "^[[:upper:]]")
cr_text <- coxph(Surv(time_until_answer, answered) ~ capital_text, data = train1)
summary(cr_text) # p=6.642e-05

#===================================================================
# if text is in all lower case
train1$cleaned <- str_replace_all(train1$text, " ", "")
train1$cleaned <- str_replace_all(train1$cleaned, "[[:punct:]]|[[:digit:]]", "")
train1$text_all_lower <- str_detect(train1$cleaned, pattern = "^[[:lower:]]+$")
cr_lower <- coxph(Surv(time_until_answer, answered) ~ text_all_lower, data = train1)
summary(cr_lower) # p=1.605e-05

#===================================================================
# prior_effort
train1$prior_effort <- str_detect(str_to_lower(train1$text), pattern = or("tried", "searched", "researched", "tested", "replaced", "used", "checked", "investigated", "considered", "measured", "attempted", "inspected", "fitted"))
cr_prior <- coxph(Surv(time_until_answer, answered) ~ prior_effort, data = train1)
summary(cr_prior) # p=0.0002236

#===================================================================
# num_prior_effort
train1$num_prior_effort <- str_count(str_to_lower(train1$text), pattern = or("tried", "searched", "researched", "tested", "replaced", "used", "checked", "investigated", "considered", "measured", "attempted", "inspected", "fitted"))
cr_numprior <- coxph(Surv(time_until_answer, answered) ~ as.factor(num_prior_effort), data = train1)
summary(cr_numprior) # p=0.000436 (lower p-value if treated as numeric)

#===================================================================
# expressing gratitude 
train1$gratitude <- str_detect(str_to_lower(train1$text), pattern = or("please", "thank you", "thanks", "thankful", "appreciate", "appreciated", "grateful"))
cr_gratitude <- coxph(Surv(time_until_answer, answered) ~ gratitude, data = train1)
summary(cr_gratitude) # p=0.0001431

#===================================================================
# greeting
train1$greeting <- str_detect(str_to_lower(train1$text), pattern = START %R% or("hey", "hello", "greetings", "hi"))
cr_greeting <- coxph(Surv(time_until_answer, answered) ~ greeting, data = train1)
summary(cr_greeting) # p=2.252e-08

#===================================================================
# update the question?
train1$update <- str_detect(train1$text, pattern = "===")
cr_up <- coxph(Surv(time_until_answer, answered) ~ update, data = train1)
summary(cr_up) # p=3.398e-09

#===================================================================
# newline ratio to length of text
train1$newline_ratio <- str_count(train1$text, pattern = "\n")/str_length(train1$text)
cr_newline <- coxph(Surv(time_until_answer, answered) ~ newline_ratio, data = train1)
summary(cr_newline) # p=1.228e-08
```

```{r, include = FALSE}
# tag-based variables
#===================================================================
# avg_tag_length
split_tags <- str_split(train1$tags, ", ", simplify = TRUE)
train1$avg_tag_length <- NA
not_na <- which(train1$tags != "")
for (i in not_na) {
  total_char <- sum(str_length(as.vector(split_tags[i,])))
  total_tags <- sum(as.vector(split_tags[i,]) != "")
  train1$avg_tag_length[i] <- total_char / total_tags
}
cr_tagl <- coxph(Surv(time_until_answer, answered) ~ avg_tag_length, data = train1)
summary(cr_tagl) # p=0.1948

#===================================================================
# maximum number of words for a question's tags
train1$max_tagwords <- rep(0, nrow(train1))
for (i in which(train1$n_tags != 0)) {
  tags <- as.vector(split_tags[i,])
  train1$max_tagwords[i] <- max(str_count(tags, pattern = "\\w+"))
}
cr_max <- coxph(Surv(time_until_answer, answered) ~ max_tagwords, data = train1)
summary(cr_max) # p=0.0001012 (should I treat this as categorical?)

#===================================================================
# frequent tags
tag_vector <- as.vector(split_tags)
tag_vector <- tag_vector[which(tag_vector != "")]
unique_tags <- unique(tag_vector)

#creating average frequency score variable
train1$tag1 <- split_tags[,1]
train1$tag2 <- split_tags[,2]
train1$tag3 <- split_tags[,3]
train1$tag4 <- split_tags[,4]

assign_score <- function(data, variable) {
  score <- rep(0, nrow(data))
  notempty <- which(data[[variable]] != "")
  for (i in notempty) {
    score[i] <- tag_freq$percent[which(tag_freq$tag == data[[variable]][i])]
  }
  return(score)
}
train1$score1 <- assign_score(train1, "tag1")
train1$score2 <- assign_score(train1, "tag2")
train1$score3 <- assign_score(train1, "tag3")
train1$score4 <- assign_score(train1, "tag4")
train1$avg_tag_score <- (train1$score1 + train1$score2 + train1$score3 + train1$score4)/as.numeric(train1$n_tags)
train1$avg_tag_score[is.nan(train1$avg_tag_score)] <- 0
cr_score <- coxph(Surv(time_until_answer, answered) ~ avg_tag_score, data = train1)
summary(cr_score) # p=2.614e-10 insanely high hazard ratio

#===================================================================
# if question contains "frequent" tag
percentile80 <- quantile(train1$avg_tag_score, probs = 0.80)

train1$frequent_tag <- FALSE
train1$frequent_tag[train1$avg_tag_score >= percentile80] <- TRUE
cr_frequent <- coxph(Surv(time_until_answer, answered) ~ frequent_tag, data = train1)
summary(cr_frequent) # p=1.814e-13

#===================================================================
# number of "frequent" tags a question contains
threshold <- 0.005
num_pop <- function(var, threshold) {
  num_pop <- rep(0, nrow(train1))
  num_pop[train1[[var]] >= threshold] <- 1
  return(num_pop)
}
numpop1 <- num_pop("score1", threshold)
numpop2 <- num_pop("score2", threshold)
numpop3 <- num_pop("score3", threshold)
numpop4 <- num_pop("score4", threshold)
train1$num_freq_tags <- numpop1 + numpop2 + numpop3 + numpop4
cr_numfreq <- coxph(Surv(time_until_answer, answered) ~ num_freq_tags, data = train1)
summary(cr_numfreq) # p=3.432e-10

#==================================================================================
#frequent terms in unanswered/answered questions
answered <- train1 %>%
  tbl_df() %>% 
  filter(answered == 1)

unanswered <- train1 %>%
  tbl_df() %>% 
  filter(answered == 0)

train1$contain_unanswered <- str_detect(as.character(train1$title), pattern = or1(freq_terms_u$word))
train1$contain_answered <- str_detect(as.character(train1$title), pattern = or1(freq_terms_a$word))

cr_unans <- coxph(Surv(time_until_answer, answered) ~ contain_unanswered, data = train1)
summary(cr_unans) # p=1.11e-16
cr_ans <- coxph(Surv(time_until_answer, answered) ~ contain_answered, data = train1)
summary(cr_ans) # p=2.314e-08
```

### Fitting model with all significant variables (univariate analysis p-value < 0.01)

##### Trying out different variable selection functions

```{r}
first <- coxph(Surv(time_until_answer, answered) ~ category + n_images + as.factor(n_tags) + as.factor(new_user) + weekday + ampm + text_length + device_length + text_contain_punct + title_questionmark + title_beginwh + capital_text + text_all_lower + prior_effort + gratitude + greeting + update + newline_ratio + max_tagwords + frequent_tag + contain_answered + contain_unanswered, data = train1)
summary(first)
AIC(first, k = 2) # 65065.88

# backwards step-wise selection with selectCox function
model1 <- pec::selectCox(Surv(time_until_answer, answered) ~ category + n_images + n_tags + new_user + weekday + ampm + text_length + device_length + text_contain_punct + title_questionmark + title_beginwh + capital_text + text_all_lower + prior_effort + gratitude + greeting + update + newline_ratio + max_tagwords + frequent_tag + contain_answered + contain_unanswered, data = train1, rule = "aic")

#results
results1 <- coxph(Surv(time_until_answer, answered) ~ category + new_user + weekday + ampm + device_length + title_questionmark + capital_text + update + contain_answered + contain_unanswered, data = train1)
AIC(results1, k = 2) #65059
summary(results1)

# backward/forward step-wise selection with stepAIC function from MASS package
model2 <- MASS::stepAIC(first, direction = "both", k = 2)
# results
results2 <- coxph(Surv(time_until_answer, answered) ~ category + n_images + as.factor(new_user) + weekday + ampm + device_length + title_questionmark + title_beginwh + capital_text + update + newline_ratio + frequent_tag + contain_answered + contain_unanswered, data = train1)
AIC(results2, k = 2) # 65050.45
summary(results2)

# best subset selection with glmulti function
# took out variables based off of p-value (function couldn't handle amount of predictors)
# model3 <- glmulti(Surv(time_until_answer, answered) ~ category + new_user + weekday + ampm + text_length + device_length + text_contain_punct + title_questionmark + capital_text + text_all_lower + prior_effort + greeting + update + newline_ratio + frequent_tag, 
#                 data = train1,
#                 level = 1, 
#                 method = "g", 
#                 crit = "aic",
#                 fitfunction = "coxph",
#                 confsetsize = 5
#                 )
# model3@formulas
# #results
# results3 <- coxph(Surv(time_until_answer,answered)~ category + new_user + weekday + ampm + device_length + title_questionmark + capital_text + update + newline_ratio + frequent_tag, data = train1)
# AIC(results3) # 65098.48
# summary(results3)

# trying out lasso regularization with the glmnet package
# library(glmnet)
# setting up matrix for function
# mx <- as.matrix(train1 %>% 
#   tbl_df() %>%
#   dplyr::select(category, n_images, n_tags, new_user, weekday, ampm, text_length, device_length, text_contain_punct, title_questionmark, title_beginwh, capital_text, text_all_lower, prior_effort, gratitude, greeting, update, newline_ratio, max_tagwords, frequent_tag, contain_answered, contain_unanswered))
# model4 <- glmnet(x, y = Surv(train1$time_until_answer, train1$answered, type = "right"), family = "cox")
# summary(model4)
# 
# x <- model.matrix( ~ rx + sex + age + obstruct + perfor + adhere + surg - 1, d)
# 
# x <- model.matrix(~ category + n_images + n_tags + new_user + weekday + ampm + text_length + device_length + text_contain_punct + title_questionmark + title_beginwh + capital_text + text_all_lower + prior_effort + gratitude + greeting + update + newline_ratio + max_tagwords + frequent_tag + contain_answered + contain_unanswered - 1, train1)
```

```{r}
# working with model from backward/forward stepwise selection
results2 <- coxph(Surv(time_until_answer, answered) ~ category + n_images + as.factor(new_user) + weekday + ampm + device_length + title_questionmark + title_beginwh + capital_text + update + newline_ratio + frequent_tag + contain_answered + contain_unanswered, data = train1) # 65050.45

# adding interaction terms
r2_i <- coxph(Surv(time_until_answer, answered) ~ category + n_images + new_user + weekday + ampm + device_length + title_questionmark + title_beginwh + capital_text + update + newline_ratio + frequent_tag + contain_answered + contain_unanswered + title_questionmark*title_beginwh + new_user*update + new_user*newline_ratio, data = train1)
AIC(r2_i, k = 2) # 65037.36
summary(r2_i)
```

@@

train1 %>%
  filter(category == "Media Player") %>%
  group_by(subcategory) %>%
  summarise(median = median(time_until_answer), n = n(), prop_a = sum(answered)/n)

@@

# renaming left over phones 
train1$new_category[train1$new_category == "Phone"] <- "Android/Other Phone"
train1$new_category[train1$new_category == "Appliance" | train1$new_category == "Household"] <- "Home"
train1$new_category[train1$new_category == "Car and Truck" | train1$new_category == "Vehicle"] <- "Vehicle"

# if there are less than 60 questions in a category, group them with other
counts <- train1 %>%
  group_by(new_category) %>%
  summarise(n = n())
for (i in which(counts$n <= 100)) {
  train1$new_category[train1$new_category == counts$new_category[i]] <- "Other"
}
table(train1$new_category)
#===================================================

# model with new_category 
final <- coxph(Surv(time_until_answer, answered) ~ new_category + n_images + new_user + weekday + ampm + device_length + title_questionmark + title_beginwh + capital_text + update + newline_ratio + frequent_tag + contain_answered + contain_unanswered + title_questionmark*title_beginwh + new_user*update + new_user*newline_ratio, data = train1)
AIC(final, k = 2) # 64728.77
summary(final)
```

@@

```{r}
#=============================================
#martingale residuals
train1$mart <- residuals(final, type = "martingale")
plot_mart <- function(var) {
  ggplot(train1, aes(x = train1[[var]], y = mart)) + 
    geom_point() + 
    geom_smooth() + 
    ggtitle(paste("Martingale Residuals for", var)) + 
    scale_x_continuous(var)
}

q_vars <- c("n_images", "device_length", "newline_ratio")
purrr::map(q_vars, plot_mart)

#=============================================
#deviance residuals 
train1$deviance <- residuals(final, type = "deviance")
ggplot(train1, aes(x = 1:nrow(train1), y = deviance)) + 
  geom_point() + 
  scale_x_continuous("Question index") + 
  scale_y_continuous(breaks = seq(-4, 4, by = 0.5))
# quite a few questions have a deviance residual of larger than 2.5

#=============================================
#schoenfeld residuals
schoen <- as.data.frame(residuals(final, type = "schoenfeld"))
# complete event times sorted from shortest to longest
schoen$comp_times <- sort(train1[train1$answered != 0,]$time_until_answer)

plot_schoen <- function(var) {
  ggplot(schoen, aes(x = comp_times, y = schoen[[var]])) + 
    geom_point() + 
    geom_smooth() + 
    ggtitle(paste("Schoenfeld Residuals for", var)) + 
    scale_y_continuous("Residuals")
}
names <- names(schoen)[-31]
purrr::map(names, plot_schoen)

#=============================================
# score residuals
score <- as.data.frame(residuals(final, type = "score"))
# function to plot score residuals
plot_score <- function(column) {
  ggplot(score, aes(x = 1:nrow(score), y = score[[column]])) + 
    geom_point() + 
    geom_smooth() + 
    ggtitle(paste("Score residuals for", column)) + 
    scale_y_continuous("Score Residuals") + 
    scale_x_continuous("Question index")
}
columns <- names(score)
purrr::map(columns, plot_score)
```

@@

@@

#356 NAs in the predictions
test_predict <- predict(final, newdata = test1, type = "risk", se.fit = TRUE)
test1$predictions <- test_predict[[1]]

@@

>>>>

```{r, echo = FALSE}
set.seed(444)
splitPlan <- vtreat::kWayCrossValidation(nrow(x), 5, NULL, NULL)
str(splitPlan)
```

@@

##### Fitting model with all significant variables (univariate analysis p-value < 0.01), select variables using stepwise functions

```{r}
first <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + contain_unanswered + title_questionmark + text_length + text_contain_punct + as.factor(num_freq_tags) + as.factor(n_tags) + contain_answered + newline_ratio + text_all_lower + update + greeting + capital_text + prior_effort + gratitude + ampm + n_images + weekday + device_length + title_beginwh, data = train1)
AIC(first, k = 2) #65294.56

# backwards step-wise selection with selectCox function
# converting to factors since function doesn't work with as.factor
train1$new_user <- as.factor(train1$new_user)
train1$num_freq_tags <- as.factor(train1$num_freq_tags)
train1$n_tags <- as.factor(train1$n_tags)

model1 <- pec::selectCox(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + text_length + text_contain_punct + num_freq_tags + n_tags + contain_answered + newline_ratio + text_all_lower + update + greeting + capital_text + prior_effort + gratitude + ampm + n_images + weekday + device_length + title_beginwh, data = train1, rule = "aic")
# results
results1 <- coxph(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + contain_answered + text_all_lower + update + ampm + device_length, data = train1)
AIC(results1, k = 2) #65285.49
summary(results1)

# backward/forward step-wise selection with stepAIC function from MASS package
model2 <- MASS::stepAIC(first, direction = "both", k = 2)
# results
results2 <- coxph(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh, data = train1)
AIC(results2, k = 2) # 65277.47
s <- summary(results2)
nrow(s$coefficients)

```

### Adding interaction terms

```{r}
# working with model from backward/forward stepwise selection

# adding interaction terms
# adding title_questionmark*title_beginwh
model2.o <- coxph(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh, data = train1)
AIC(model2.o, k = 2) # 65274.49
oshitar::compare_nested(model2.o, results2)

# adding new_user*update
model2.o1 <- coxph(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + new_user*update, data = train1)
AIC(model2.o1, k = 2) # 65272.55
oshitar::compare_nested(model2.o1, results2)

# adding new_user*ampm 
model2.o2 <- coxph(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + new_user*ampm, data = train1)
AIC(model2.o2, k = 2) # 65271.84
oshitar::compare_nested(model2.o2, results2)

# all signficant interaction terms 
model_i <- coxph(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh + new_user*update + new_user*ampm, data = train1)
AIC(model_i, k = 2) # 65263.35
```

@@

train1 %>%
  filter(new_category == "Electronics") %>%
  group_by(subcategory) %>%
  summarise(median = median(time_until_answer), n = n(), prop_a = sum(answered)/n) %>%
  arrange(median)

train1 %>%
  group_by(new_category) %>%
  summarise(median = median(time_until_answer), n = n(), prop_a = sum(answered)/n) %>%
  arrange(median)

@@

# renaming left over phones 
train1$new_category[train1$new_category == "Phone"] <- "Android/Other Phone"
# merge household and appliance into "Home"
train1$new_category[train1$new_category == "Appliance" | train1$new_category == "Household"] <- "Home"
# merging Car and Truck with Vehicle 
train1$new_category[train1$new_category == "Car and Truck" | train1$new_category == "Vehicle"] <- "Vehicle"

# if there are less than 100 questions in a category, group them with other
counts <- train1 %>%
  group_by(new_category) %>%
  summarise(n = n())
for (i in which(counts$n <= 100)) {
  train1$new_category[train1$new_category == counts$new_category[i]] <- "Other"
}
table(train1$new_category)
#===================================================

model_new <- coxph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh, data = train1)
AIC(model_new, k = 2) #64999.87

#new_cateogry*new_user
#new_cateogry*
model_new1 <- coxph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + new_category*new_user, data = train1)
AIC(model_new1, k = 2) # 64994.49
oshitar::compare_nested(model_new1, model_new)

# model with ALL interactions
# model with new_category
model_full <- coxph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh + new_user*update + new_user*ampm + new_category*new_user, data = train1)
AIC(model_full, k = 2) # 64978.87
summary(model_full)
```

@@

* Martingale residuals
    + plot for each continuous predictor 
    + assess adequacy of functional form of predictors, or suggest a potential form 
* Deviance residuals
    + check for outliers identify questions poorly predicted by the model 
    + one plot, examine questions with |residuals| > 2.5
* Schoenfeld residuals
    + one plot for each predictor 
    + if loess curve is flat, proportional hazard assumption is not violated, doesn't depend on time. Distinct pattern indicates violation of this assumption
    + **from the plots:** new_user, title_questionmark, num_freq_tags (1), ampm (Morning, Night), weekday (Thursday, Saturday), new_user*AMPM (morning, night) may violate PH assumption 
* Score residuals
    + check for influential observations. ID quesitons who's predictor values highly effect parameter estimates
    + plot for each predictor 
* **figure out how to identify certain points on ggplots**
* statified on new_category, AIC dropped drastically. But this means that I can't compare the different groups in new_category 
```{r}
#=============================================
#martingale residuals
train1$mart <- residuals(model_full, type = "martingale")

ggplot(train1, aes(x = device_length, y = mart)) + 
  geom_point() + 
  geom_smooth() + 
  ggtitle(paste("Martingale Residuals for device_length")) + 
  scale_x_continuous("Device_length")

#=============================================
#deviance residuals 
train1$deviance <- residuals(model_full, type = "deviance")
ggplot(train1, aes(x = 1:nrow(train1), y = deviance)) + 
  geom_point() + 
  scale_x_continuous("Question index") + 
  scale_y_continuous(breaks = seq(-4, 4, by = 0.5))
# quite a few questions have a deviance residual of larger than 2.5

#=============================================
#schoenfeld residuals
schoen <- as.data.frame(residuals(model_full, type = "schoenfeld"))
# complete event times sorted from shortest to longest
schoen$comp_times <- sort(train1[train1$answered != 0,]$time_until_answer)

plot_schoen <- function(var) {
  ggplot(schoen, aes(x = comp_times, y = schoen[[var]])) + 
    geom_point() + 
    geom_smooth() + 
    ggtitle(paste("Schoenfeld Residuals for", var)) + 
    scale_y_continuous("Residuals")
}
names <- names(schoen)[-ncol(schoen)]
purrr::map(names, plot_schoen)

#=============================================
# score residuals
score <- as.data.frame(residuals(model_full, type = "score"))
# function to plot score residuals
plot_score <- function(column) {
  ggplot(score, aes(x = 1:nrow(score), y = score[[column]])) + 
    geom_point() + 
    geom_smooth() + 
    ggtitle(paste("Score residuals for", column)) + 
    scale_y_continuous("Score Residuals") + 
    scale_x_continuous("Question index")
}
columns <- names(score)
purrr::map(columns, plot_score)

#=============================================
# formal test of PH assumption
ph_test <- data.frame(predictors = rownames(cox.zph(model_full)$table), cox.zph(model_full)$table) 
rownames(ph_test) = NULL
ph_test <- ph_test %>%
  arrange(p)

# stratifying on new_category
strat_model <- coxph(Surv(time_until_answer, answered) ~ strata(new_category) + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh + new_user*update + new_user*ampm, data = train1)
AIC(strat_model, k = 2) # 49766.8
summary(strat_model)

# stratifying on new_user
strat_model1 <- coxph(Surv(time_until_answer, answered) ~ new_category + strata(new_user) + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh, data = train1)
AIC(strat_model1, k = 2) # 60543.75
summary(strat_model1)

# final model: stratified on new_category
final <- strat_model
```

@@

##### variable set up in test data

* categorical variables must be the same across data sets, but I want the categorical variable to change with each data set, any way to do this?

@@

#=============================================
# predicting on the test data

#356 NAs in the predictions
test_predict <- predict(model_full, newdata = test1, type = "risk", se.fit = TRUE)
test1$predictions <- test_predict[[1]]

@@

```{r}
# function to set up variables for test data 
variable_setup <- function(data) {
  data$category <- as.character(data$category)
  data$category[is.na(data$category)] <- "Other"

  data$new_category <- data$category
  apple_terms <- c("apple", "ipod", "ipad")
  data$apple <- str_detect(str_to_lower(data$device), pattern = START %R% or1(apple_terms) %R% SPC)
  data$new_category[data$apple == TRUE | data$subcategory == "iPhone" | data$category == "Mac"] <- "Apple Product"
  data$new_category[data$new_category == "Phone"] <- "Android/Other Phone"
  data$new_category[data$new_category == "Appliance" | data$new_category == "Household"] <- "Home"
  data$new_category[data$new_category == "Car and Truck" | data$new_category == "Vehicle"] <- "Vehicle"
  data$new_category[data$new_category == "Computer Hardware" | data$new_category == "Media Player" |
                     data$new_category == "Apparel"] <- "Other"
  #=============================================
  #weekday
  data$datetime <- as.POSIXct(data$post_date,origin="1970-01-01")
  data$weekday <- factor(weekdays(data$datetime), levels = c("Monday", "Tuesday", "Wednesday", 
                                                             "Thursday", "Friday", "Saturday", "Sunday"))
  #=============================================
  #ampm
  data$hour <- as.numeric(format(data$datetime,"%H"))
  data$ampm <- "Night"
  data$ampm[data$hour >= 5 & data$hour < 12] <- "Morning"
  data$ampm[data$hour >= 12 & data$hour < 17] <- "Afternoon" #noon - 5pm
  data$ampm[data$hour >= 17 & data$hour < 20] <- "Evening" #5pm - 8pm
  #=============================================
  # text length
  data$text_length <- str_length(data$text)
  #=============================================
  # device name length
  data$device_length <- str_length(data$device)
  #=============================================
  # if the title ends with a question mark
  library(rebus)
  data$title_questionmark <- str_detect(data$title, pattern = QUESTION %R% END)
  #=============================================
  # if title begins with "wh"
  data$title_beginwh <- str_detect(str_to_lower(data$title), pattern = "^wh")
  #=============================================
  data$capital_text <- str_detect(as.character(data$text), pattern = "^[[:upper:]]")
  #=============================================
  data$update <- str_detect(data$text, pattern = "===")
  #=============================================
  data$newline_ratio <- str_count(data$text, pattern = "\n")/str_length(data$text)
  #=============================================
  # frequent tags
  split_tags <- str_split(data$tags, ", ", simplify = TRUE)
  tag_vector <- as.vector(split_tags)
  tag_vector <- tag_vector[which(tag_vector != "")]
  unique_tags <- unique(tag_vector)

  #creating average frequency score variable
  data$tag1 <- split_tags[,1]
  data$tag2 <- split_tags[,2]
  data$tag3 <- split_tags[,3]
  data$tag4 <- split_tags[,4]

  assign_score <- function(data, variable) {
    score <- rep(0, nrow(data))
    notempty <- which(data[[variable]] != "")
    for (i in notempty) {
      score[i] <- tag_freq$percent[which(tag_freq$tag == data[[variable]][i])]
    }
    return(score)
  }
  data$score1 <- assign_score(data, "tag1")
  data$score2 <- assign_score(data, "tag2")
  data$score3 <- assign_score(data, "tag3")
  data$score4 <- assign_score(data, "tag4")
  data$avg_tag_score <- (data$score1 + data$score2 + data$score3 + 
                            data$score4)/as.numeric(data$n_tags)
  data$avg_tag_score[is.nan(data$avg_tag_score)] <- 0
  #=============================================
  # if question contains "frequent" tag
  percentile80 <- quantile(data$avg_tag_score, probs = 0.80)

  data$frequent_tag <- FALSE
  data$frequent_tag[data$avg_tag_score >= percentile80] <- TRUE
  #=============================================
  #frequent terms in unanswered/answered questions
  answered <- data %>%
      tbl_df() %>% 
      filter(answered == 1)
  unanswered <- data %>%
    tbl_df() %>% 
    filter(answered == 0)

  data$contain_unanswered <- str_detect(as.character(data$title), pattern = or1(freq_terms_u$word))
  data$contain_answered <- str_detect(as.character(data$title), pattern = or1(freq_terms_a$word))

  data$new_user <- as.factor(data$new_user)

  return(data)
}

```
